---
title: "Algerian Housing EDA"
output: html_notebook
---

Now that we have the data from both websites `ouedkniss` and `lkeria`

### Preparations {.tabset .tabset-fade .tabset-pills}

#### Loading the packages
```{r message=FALSE, warning=FALSE}
library(tidyverse) #data manipulation and visualization
library(stringr) #string manipulation
library(lubridate) #date & time manipulation
```

#### Loading the data
```{r message=FALSE, warning=FALSE}
lkeria <- read_csv("algiers_lkeria.csv")
ouedkniss <- as_tibble(read.csv("Housing_Data26072018.csv"))
```

### Structure {.tabset .tabset-fade .tabset-pills}

As a first step let's have an overview of our data.

#### Lkeria

```{r}
glimpse(lkeria)
```

#### Ouedkniss

```{r}
ouedkniss %>% 
  select(ID.Offer, Date, Hour, Month, Municipality, lon, lat, 
         Nb.Floor:Nb.Views, Area, Garage:Payment, Price.value.dzd, District, Top_Municipalities,
         Announcer.Name, Announcer.Type, Store.Municipality, Store.lon, Store.lat) %>% 
  glimpse()
```



#### Reformatting lkeria data

```{r echo=TRUE, message=FALSE, warning=FALSE}
lkeria <- lkeria %>% 
  filter(type == "Appartement") %>% 
  mutate(Nb.floor = as.integer(floor_nbr),
         Top_Municipalities = fct_lump(district, 9),
         Announcer.Type = word(agency_name, 1, 2),
         price_m2 = price/surface, 
         Garage = str_detect(details, "Garage"),
         Garden = str_detect(details, "Jardin"),
         Furnished = str_detect(details, "Meublé")) %>% 
  rename(Date = dates,
         Nb.Room = nbr_rooms,
         Municipality = district,
         Area = surface,
         Price.value.dzd = price)
glimpse(lkeria)
```

###

- For `ouedkniss` data, we selected 25 relevent variables out of 50 for our analysis.

- We reformatted some variables in lkeria dataset so it can be combined with ouedkniss dataset.

- If we explore the Top_Municipalities, we notice that some municipalities are not in common for both datasets.

### {.tabset .tabset-fade .tabset-pills}

#### Lkeria Top Municipalities
```{r}
lkeria %>% 
  group_by(Top_Municipalities) %>% 
  summarise(n = n()) %>% 
  arrange(desc(n))
```

#### Ouedkniss Top Municipalities

```{r}
ouedkniss %>% 
  group_by(Top_Municipalities) %>% 
  summarise(n = n()) %>% 
  arrange(desc(n))
```

###
- We notice from the code above that not all *Top Municpalities* are in common for both datasets and since we have fewer data for `Lkeria`.
- for a fair comparison, we'll create a new variable **price per meter squared**, we'll also adapt `Ouedkniss`'s *Top Municipalities* to match those of `Lkeria`.

```{r}
ouedkniss <- ouedkniss %>% 
  mutate(price_m2 = Price.value.dzd/Area, 
         Top_Municipalities_new = case_when(Municipality == "EL ACHOUR" ~ "El Achour",
                                            Municipality == "OULED FAYET" ~ "Ouled Fayet",
                                            Municipality == "HYDRA" ~ "Hydra",
                                            Municipality == "BIR KHADEM" ~ "Birkhadem",
                                            Municipality == "CHERAGA" ~ "Cheraga",
                                            Municipality == "ALGER" ~ "Alger-Centre",
                                            Municipality == "KOUBA" ~ "Kouba",
                                            Municipality == "BIR MOURAD RAIS" ~ "Bir Mourad Rais",
                                            Municipality == "MOHAMMADIA" ~ "Mohammadia",
                                            TRUE ~ "Other"))
```

Normalement rana segamna wach nehtajou

Now, let's explore some hypothesis about data
We'll draw a boxplot to compare the prices across both websites by number of rooms.

First of all, we need to combine our data
```{r}
ouedkniss_1 <- ouedkniss %>% 
  filter(Nb.Room %in% c(3:5), Announcer.Type %in% c("AGENCE")) %>%
  select(Nb.Room, price_m2, Top_Municipalities_new) %>% 
  mutate(website = "ouedkniss") %>% 
  rename(Top_Municipalities = Top_Municipalities_new)

lkeria_1 <- lkeria %>% 
  filter(Nb.Room %in% c(3:5), Announcer.Type == "Agence immobilière") %>% 
  mutate(website = "lkeria") %>% 
  select(Nb.Room, price_m2, Top_Municipalities, website)

combined_data <- rbind(ouedkniss_1, lkeria_1)

combined_data <- combined_data %>% 
  filter(!is.na(price_m2), price_m2 <= 7.5e5)
```

```{r}
combined_data %>% 
  ggplot(aes(x = website, y = price_m2, fill = website)) +
  geom_boxplot() +
  facet_wrap(~ Nb.Room)
```

We have excluded rows with missing prices and above *750000 DZD* to avoid potential errors in data and some outliers. we also considered only houses which number of rooms varies from 3 to 5 as they are the most common categories.

from this graph, we notice that housing prices in `Lkeria` are **higher** than those listed in `Ouedkniss` for all three categories.
The median price values in our sample data are:
```{r}
tapply(combined_data$price_m2, combined_data$website, median)
```
On average, lkeria's prices are higher by approximately **+19%**.

Now let's see the variation of prices across different locations

```{r}
combined_data %>% 
  ggplot(aes(x = website, y = price_m2, fill = website)) +
  geom_boxplot(show.legend = FALSE) +
  facet_wrap(~ Top_Municipalities, nrow = 2)
```

This graph shows a comparison by top municipalities. The prices of `Lkeria` are higher for most locations (except for *Bir Mourad Rais* and *Mohammadia*). Kouba has the highest interquartile range IQR, this is very likely due to an error in our data, more investigations are needed to explain this shape.

```{r}
combined_data %>% 
  ggplot(aes(x = Top_Municipalities, y = price_m2, fill = Top_Municipalities)) +
  geom_boxplot(show.legend = FALSE) +
  facet_wrap(~ website, nrow = 2)
```

Another hypothesis made about this data is that the announcer type has a significant impact on the price. Let's investigate more by plotting price distributions by *Announcer Type* using `ouedkniss` dataset.


```{r message=FALSE}
ouedkniss %>% 
  filter(!is.na(price_m2), price_m2 <= 7.5e5, Nb.Room %in% c(3:5), Announcer.Type!= "PROMOTEUR") %>% 
  ggplot(aes(x = Announcer.Type, y = price_m2, fill = Announcer.Type)) +
  geom_boxplot()
  
```


The graph shows that **bureau d'affaire** prices are slightly higher than **housing agencies** ("AGENCE") prices. The **individual offers** ("PARTICULIER") have lower prices. 

The median price values for those categories are *205555.6*, *219649.1*, *161290.3 DZD* respectively. So on average, "BUREAU D'AFFAIRE" prices are more expensive by **+6%** compared to "AGENCE" and by **+36%** compared to "PARTICULIER".

Next, we compare the prices of "BUREAU D'AFFAIRE" from `ouedkniss` to "AGENCE" prices from `lkeria`.

```{r}
ouedkniss_2 <- ouedkniss %>% 
  filter(Nb.Room %in% c(3:5), Announcer.Type %in% c("BUREAU D'AFFAIRE")) %>%
  select(Nb.Room, price_m2, Top_Municipalities_new) %>% 
  mutate(website = "ouedkniss") %>% 
  rename(Top_Municipalities = Top_Municipalities_new)

combined_data_2 <- rbind(ouedkniss_2, lkeria_1)

combined_data_2 <- combined_data_2 %>% 
  filter(!is.na(price_m2), price_m2 <= 7.5e5)
```

```{r}
combined_data_2 %>% 
  ggplot(aes(x = website, y = price_m2, fill = website)) +
  geom_boxplot() +
  facet_wrap(~ Top_Municipalities, nrow = 2) +
  labs(title = " AGENCE(Lkeria) VS. BUREAU D'AFFAIRE(Ouedkniss)")
```

Even that the "BUREAU D'AFFAIRE" offers the most expensive flats as we have seen earlier, according to this graph, lkeria's "housing agencies" provide higher prices for most municipalities.


